Emulation of high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2022-09-12 intro.tex
start writing about factorisation

    is a dimensional free parameter of the theory, usually
    written as

@@

    The coupling in QCD is dependent on the energy scale
    of the process, $\mu$. The behaviour of $\alpha_{\mathrm{s}}$

@@

@@

>>>>

    is a dimensionless free parameter of the theory.
    It is common to use the strong coupling constant
    instead, 

@@

    The strong coupling constant, is not constant, but
    is dependent on the energy scale of the process, $\mu$.
    The behaviour of $\alpha_{\mathrm{s}}$

@@

    Another consequence of the running coupling
    is colour confinement, in which quarks and
    gluons cannot exist as free particles. Due
    to the increasing strength of coupling at low
    energies, quarks and gluons are forced to
    form composite, colourless particles, known as
    hadrons. The most common example of a hadron
    is the proton which is the origin of the name
    Large Hadron Collider.

@@

\section{Factorisation theorem}
    At the LHC, collisions occur between two protons,
    which have constituent quarks and gluons.
    The application of QCD to describe phenomenon
    in these proton-proton collisions rests on the use of
    the factorisation theorem which enables the
    separation of `soft' and `hard' energy scales.
    Within the proton, there are composite quarks
    and gluons that are constantly absorbed and
    emitted. However, during a high energy collision
    of two protons, the constituent quarks and gluons are
    effectively frozen due to the extremely high
    energy of the collision.
    The `soft' energy scales refers to the quarks
    and gluons residing inside a proton and the `hard'
    energy scale refers to the energetic collision.

    The production of particles from a hadronic collision,
    the hadronic cross-section can therefore be
    written as
    ...
